---
title: "Assignment 3: parallel computing "
author: "Stijn Hanssen"
date: "Oktober 2018"
output: html_document
---

### Clear working space
First step is to make sure that the working space is empty.
```{r}
# clear all variables
rm(list=ls()) 
```

### Set path working directory
The directory path is set to the stored datasets.
```{r}
# set working directory
setwd("C:/Users/stijn/Desktop/Master systems biology/Systems biology year 2/scientific computing/parallelprocessing") 
```

### Load libraries
Loading the required packages for specific functions. 
```{r}
options(java.parameters = "-Xmx8g")
# for proper nextElem() support
library(itertools) 
# access functionality of Java framework
library(rcdk)
# provides a parallel backend for the dopar function
library(doParallel)
```

### Import data

```{r}
# total amount molecules in sdf file
max_n_molecules = 377550
# amount molecules imported
n = 1000
# iload.molecules: iterating version of loader
iter <- iload.molecules('C:/Users/stijn/Desktop/Master systems biology/Systems biology year 2/scientific computing/parallelprocessing/aid624202.sdf', type='sdf')
# text progress bar
pb <- txtProgressBar(min = 0, max = n , style = 3)
# initiate value
counter = 0 
# set a list
mols = list()
# while loop to iterate until n is reached
while(hasNext(iter)) {
counter = counter + 1
# generic function to prodcue values, save values in mols    
    mols[[counter]] <- nextElem(iter)
setTxtProgressBar(pb,counter)
if(counter == n){
    break
  }
}
close(pb)
```

### list descriptors
```{r}
# list descriptors wanted to calculate
descNames <- unique(unlist(sapply(get.desc.categories()[2:4], get.desc.names)))
```

### Convert into smiles

```{r}
# produce vector containing the atomic components
mols = unlist(mols)
# function generate smiels representation of IAtomContainer object
smiles = lapply(mols,get.smiles)
```

### Parallel computing
distribute among cores. convert smiles, export to cores, parse smiles to molecules.
```{r}

```

### Plot

```{r}

```
